% Copyright 2013 Christophe-Marie Duquesne <chmd@chmd.fr>
% Copyright 2014 Mark Szepieniec <http://github.com/mszep>
% 
% ConText style for making a resume with pandoc. Inspired by moderncv.
% 
% This CSS document is delivered to you under the CC BY-SA 3.0 License.
% https://creativecommons.org/licenses/by-sa/3.0/deed.en_US

\startmode[*mkii]
  \enableregime[utf-8]  
  \setupcolors[state=start]
\stopmode

\setupcolor[hex]
\definecolor[titlegrey][h=757575]
\definecolor[sectioncolor][h=397249]
\definecolor[rulecolor][h=9cb770]

% Enable hyperlinks
\setupinteraction[state=start, color=sectioncolor]

\setuppapersize [A4][A4]
\setuplayout    [width=middle, height=middle,
                 backspace=20mm, cutspace=0mm,
                 topspace=10mm, bottomspace=20mm,
                 header=0mm, footer=0mm]

%\setuppagenumbering[location={footer,center}]

\setupbodyfont[11pt, helvetica]

\setupwhitespace[medium]

\setupblackrules[width=31mm, color=rulecolor]

\setuphead[chapter]      [style=\tfd]
\setuphead[section]      [style=\tfd\bf, color=titlegrey, align=middle]
\setuphead[subsection]   [style=\tfb\bf, color=sectioncolor, align=right,
                          before={\leavevmode\blackrule\hspace}]
\setuphead[subsubsection][style=\bf]

\setuphead[chapter, section, subsection, subsubsection][number=no]

%\setupdescriptions[width=10mm]

\definedescription
  [description]
  [headstyle=bold, style=normal,
   location=hanging, width=18mm, distance=14mm, margin=0cm]

\setupitemize[autointro, packed]    % prevent orphan list intro
\setupitemize[indentnext=no]

\setupfloat[figure][default={here,nonumber}]
\setupfloat[table][default={here,nonumber}]

\setuptables[textwidth=max, HL=none]

\setupthinrules[width=15em] % width of horizontal rules

\setupdelimitedtext
  [blockquote]
  [before={\setupalign[middle]},
   indentnext=no,
  ]


\starttext

\section[stefanos-georgiou]{Stefanos Georgiou}

\thinrule

\startblockquote
{\bf Contact details}: stefanos1316 at gmail dot com, sgeorgiou at aueb
dot gr, stefanos dot g at allcancode dot com
\stopblockquote

\startblockquote
{\bf About me}: I am passionated with
\useURL[url1][https://stefanos1316.github.io/programmers_blog/][][coding]\from[url1],
empirical studies, integrating new technologies, and automating
cumbersome tasks. On my free time, I enjoy sporting, reading books, and
\useURL[url2][https://stefanos1316.github.io/my_blog/index.html][][travelling]\from[url2].
\stopblockquote

\thinrule

\subsection[education]{Education}

\startdescription{2016-2020}
  {\bf PhD, Computer Science}; Athens University of Economics and
  Business

  Thesis title: {\em Energy and Run-Time Performance Practices in
  Software Engineering};
  \useURL[url3][phd_thesis.pdf][][Thesis]\from[url3]

  PhD advisors:
  \useURL[url4][https://www2.dmst.aueb.gr/dds/][][Prof.~Diomidis
  Spinellis]\from[url4] and
  \useURL[url5][https://www.balab.aueb.gr/panos-panagiotis-louridas.html][][Prof.~Panos
  Louridas]\from[url5]
\stopdescription

\startdescription{2013-2015}
  {\bf MSc, Pervasive Computing and Communications for Sustainable
  Development (PERCCOM)}; Erasmus Mundus Joint Master Degree

  ITMO University of Saint-Petersburg (Russia) Thesis title:
  {\em Implementating Green IT Approach for Transferring Big Data over
  Parallel Data Links};
  \useURL[url6][msc_thesis.pdf][][Thesis]\from[url6]

  Lulea University of Technology (Sweden) Semester 3: {\em Resource
  Efficient Pervasive Computing Systems and Communications}
  \useURL[url7][msc_lulea.pdf][][Degree]\from[url7]

  Lappeenranta University of Technology (Finland) Semester 2: {\em Smart
  Software and Services}
  \useURL[url8][msc_lappeenranta.pdf][][Degree]\from[url8]

  Unversity of Lorraine (France) Semester 1: {\em Sustainable Computer
  Network Engineering}
  \useURL[url9][msc_lorraine.pdf][][Degree]\from[url9]
\stopdescription

\startdescription{2008-2013}
  {\bf BSc, Networks and Systems Programming}; University of Cyprus

  Thesis title: {\em Implementation and Evaluation of the Biologically
  -- Inspired AntHocNet Routing Protocol in Sensor Network};
  \useURL[url10][bsc_cyprus.pdf][][Degree]\from[url10]
\stopdescription

\subsection[research-publications]{Research Publications}

\startitemize[packed]
\item
  Conference Papers
  \startitemize[packed]
  \item
    {\bf Stefanos Georgiou}, Maria Kechagia Panos Louridas, and Diomidis
    Spinellis. What Are Your Programming Language's Energy-Delay
    Implications? In 15th International Conference on Mining Software
    Repositories: Technical Track, MSR '18. New York, NY, USA, May 2018.
    Association for Computing Machinery.
    {[}\useURL[url11][GKLS18.pdf][][Paper]\from[url11]{]}
    {[}\useURL[url12][GKLS18.bib][][BibTex]\from[url12]{]}
    {[}\useURL[url13][https://www.slideshare.net/GeorgiouStefanos/what-are-your-programming-languages-energydelay-implications-106251480][][Presentation]\from[url13]{]}
    {[}\useURL[url14][https://github.com/stefanos1316/Rosetta_Code_Data_Set][][Data-set]\from[url14]{]}
  \item
    {\bf Stefanos Georgiou}, Maria Kechagia, and Diomidis Spinellis.
    Analyzing Programming Languages' Energy Consumption: An Empirical
    Study. In PCI 2017: Proceedings of the 21st Pan-Hellenic Conference
    on Informatics, ACM International Conference Proceeding Series. ACM
    Press, September 2017.
    {[}\useURL[url15][GKS17.pdf][][Paper]\from[url15]{]}
    {[}\useURL[url16][GKS17.bib][][BibTex]\from[url16]{]}
    {[}\useURL[url17][https://www.slideshare.net/GeorgiouStefanos/programming-languages-energy-consumption-an-empirical-study][][Presentation]\from[url17]{]}
    {[}\useURL[url18][https://github.com/stefanos1316/Rosetta_Code_Data_Set][][Data-Set]\from[url18]{]}
  \stopitemize
\item
  Journal Articles
  \startitemize[packed]
  \item
    {\bf Stefanos Georgiou}, Dimitris Mitropoulos, and Diomidis
    Spinellis. Energy-Efficient Computing in a Secure Environment.
    Submitted in July 2020 for review in ACM Transaction of Computer
    Systems.
  \item
    {\bf Stefanos Georgiou} and Diomidis Spinellis. Energy-Delay
    Investigation of Remote Inter-Process Communication Technologies.
    Accepted for publication in Elsevier Journal of Systems and Software
    2019. {[}\useURL[url19][GS19.pdf][][Preprint]\from[url19]{]}
    {[}\useURL[url20][GS19.bib][][BibTex]\from[url20]{]}
  \item
    {\bf Stefanos Georgiou}, Stamatia Rizou, and Diomidis Spinellis.
    Software Development Life Cycle for Energy-Efficiency: Techniques
    and Tools. Accepted for publication in ACM Computing Surveys 2019.
    {[}\useURL[url21][GRS19.pdf][][Preprint]\from[url21]{]}
    {[}\useURL[url22][GRS19.bib][][BibTex]\from[url22]{]}
  \stopitemize
\stopitemize

\subsection[invited-talks]{Invited Talks}

\startdescription{Tutorials}
  {\em How to improve your CI/CD process} presented on 5th of July 2019
  at BALab of Athens University of Economics and Business in Athens,
  Greece.
  \useURL[url23][https://aueb-balab.github.io/courses/tools/ci_cd_with_gitlab-p.html\#/][][Presentation]\from[url23]

  {\em Travis CI with CV template tutorial} presented on 7th of June
  2018 at ITMO Univesity of Saint Petersburg for PERCCOM Master students
  in Saint-Petersburg, Russia.
  \useURL[url24][https://aueb-balab.github.io/courses/tools/travis_ci_cv_template-p.html\#/][][Presentation]\from[url24]
\stopdescription

\startdescription{Research}
  {\em What are your programming language's energy-delay implications?}
  presented on 12th of June 2018 at PERCCOM's Summer School in
  Lappeenranta, Finland.
  \useURL[url25][perccom_summer_school_2018.pdf][][Proof]\from[url25]
\stopdescription

\subsection[organization-services]{Organization Services}

\startdescription{{\em Program Committee}}
  International Workshop on Sustainable Software Engineering
\stopdescription

\startdescription{{\em Reviewer}}
  Jounals submitted to Software: Practices and Experience
\stopdescription

\startdescription{{\em Co-reviewer}}
  Conference papers submitted to ICSE-SEIP, MSR, OSS, ICPC, ICCS, SANER,
  and SATToSE
\stopdescription

\subsection[teaching-experience]{Teaching Experience}

Assisting my PhD advisor at Programming II course (Winter Semester of
2016, 2017, and 2018) by giving tutorial and Lab sessions in Java
{[}\useURL[url26][https://github.com/AUEB-BALab/courses][][Repository]\from[url26]{]}

Gave Java lectures and tutorials for the 1st and 2nd Coding Boot Camp in
Athens, Greece (Oct. 2017 - May 2018)
{[}\useURL[url27][https://github.com/codeandwork/courses][][Repository]\from[url27]{]}
{[}\useURL[url28][boot_camp_athens_2016_2017.pdf][][Proof]\from[url28]{]}

\subsection[industrial-experience]{Industrial Experience}

\startdescription{Jan 2019-Apr 2020}
  {\bf Back-end developer, DevOps, and Integrations:}
  \useURL[url29][https://www.allcancode.com/][][AllCanCode Inc. Greek
  Branch]\from[url29]

  Developing in Node.JS, integrating new services (API end-points), and
  setting up the cloud infrasture and projects development workflow.
\stopdescription

\startdescription{Jan 2016-2019}
  {\bf Proposals writing:}
  \useURL[url30][https://portal.singularlogic.eu/en][][Singular Logic
  S.A.]\from[url30]

  Proposals writing and participating in project's telco meetings for
  the European Projects Department.
\stopdescription

\subsection[technical-experience]{Technical Experience}

\startdescription{{\em Back-End}}
  BASH (Often automating cumbersome and time consuming tasks)

  NodeJS (Fan of KOA, prefer Mocha-Chai, like to use Native Addons for
  performance)

  Java (First real love, I was also teaching it at the Athes University
  of Economics and Business)

  Python (No need to read tutorials, feeling confy to code anytime)

  C (First ever learned, in love with Makefiles, and impressed by its
  performance)

  C++ (Second to learn after C, but as soon as I learned Java I stopped
  using it)

  MongoDB (Queries, Aggregations, and Optimizations)
\stopdescription

\startdescription{{\em DevOps}}
  Continuous Integration and Deployment (Big fan of CI/CD Travis,
  GitLab, and Actions)

  Code Quality (Coveralls, maven-plugins, Style-Checkers, and Reports)

  Hosting (Firbase, Docker, Google App Engine, and lover of Cloud
  Functions)

  Mobile CI/CD (Bitrise supporter for Cordova and slightly Flutter user)

  Configuration Management (Ansible because it uses YAML)
\stopdescription

\startdescription{{\em Projects}}
  Epidose: A privacy-preserving epidemic dosimeter based on contact
  tracing
  \useURL[url31][https://github.com/eellak/epidose][][Repository]\from[url31]

  Exam Questionnaire Scanner:
  \useURL[url32][https://github.com/AntonisGkortzis/ExamQuestionnaireScanner][][Repository]\from[url32]

  Measuring Energy Consumption:
  \useURL[url33][https://github.com/stefanos1316/SEMTs_Comparisson][][Software]\from[url33]
  and
  \useURL[url34][https://stefanos1316.github.io/courses/tools/measuring_energy_consumption_direct_approach-p.html\#/][][Hardware]\from[url34]
  tools

  Programming II website:
  \useURL[url35][https://github.com/stefanos1316/courses][][Repository]\from[url35]

  Rosetta Code Experiement:
  \useURL[url36][https://github.com/stefanos1316/Rosetta_Code_Research_MSR][][Repository]\from[url36]

  Validate Links:
  \useURL[url37][https://github.com/stefanos1316/validateLinks][][Repository]\from[url37]
\stopdescription

\startdescription{{\em Certificates}}
  Unix Tools: \useURL[url38][unix_tools_edx.pdf][][Data, Software, and
  Production Engineering]\from[url38]

  MongoDB: \useURL[url39][mongodb_m001.pdf][][Basics]\from[url39],
  \useURL[url40][mongodb_m121.pdf][][Aggregation]\from[url40],
  \useURL[url41][mongodb_m220.pdf][][JavaScript]\from[url41],
  \useURL[url42][mongodb_m201.pdf][][Performance]\from[url42]
\stopdescription

\starttyping
<!-- Loading stuff -->
Loading the data just for you.
\stoptyping

\subsection[grands-awards-languages-and-living-abroad]{Grands, Awards,
Languages, and Living Abroad}

\startitemize[packed]
\item
  Grands and awards:
  \startitemize[packed]
  \item
    Mentored younger researcher \useURL[url43][fse19.pdf][][who won
    2nd]\from[url43] place in SRC ESEC/FSE '19.
  \item
    Best paper award from the 15th Annual DMST Student Conference (2018)
  \item
    Marie Skłodowska-Curie funds,
    \useURL[url44][https://portal.singularlogic.eu/en/eu-project/12374/seneca][][SENECA]\from[url44]
    (2016-2019)
  \item
    Erasmus Mundus Masters Scholarship, PERCCOM (2013-2015)
  \stopitemize
\item
  Human Languages:
  \startitemize[packed]
  \item
    Greek/Hungarian (Native speaker)
  \item
    English (Fluent speaker)
  \item
    Russian/France (Basic knowledge)
  \stopitemize
\item
  Living Abroad:
  \startitemize[packed]
  \item
    Born in Gyula, Hungary but grown up in Nicosia, Cyprus.
  \item
    Ate baguettes and drunk wine in Lorraine, France (Fall Semester of
    2013)
  \item
    Attended to many sauna parties in Lappeenranta, Finland (Spring
    Semester of 2014)
  \item
    Fish ice-cold beers from lakes in Lulea, Sweden (Fall Semeseter of
    2014)
  \item
    Drunk vodka and ate borsh in Saint-Petersburg, Russia (Spring
    Semester of 2015)
  \item
    Teaching in Athens and visiting islands in Greece (Fall Semester of
    2016 till now)
  \item
    Biked in Delft, the Netherlands for my PhD secondment (Half month of
    Sept. 2017)
  \stopitemize
\stopitemize

\thinrule

\startblockquote
<sgeorgiou@aueb.gr, stefanos.g@allcancode.com>\crlf
Troias 2, ground floor, second floor - Athens, Greece
\stopblockquote

\stoptext
